---
title: "Final Project"
subtitle: "EPIB 677, Winter 2020, McGill University"
author: "Zharmaine Ante, Demy Dam, Ornella Wafo Noubissie" 
date: "`r Sys.Date()`"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r include = FALSE}
## ---- Setup ------------------------------------------------------------------
knitr::opts_chunk$set(
  echo = TRUE,           # show code
  warning = FALSE,       # don't show warnings
  message = FALSE,       # don't show messages (less serious warnings)
  cache = FALSE,         # set to TRUE to save results from last compilation
  fig.align = "center",  # center figures
  fig.asp = 1,           # fig.aspect ratio
  fig.width = 4          # fig width
)
```

# Abstract (1 page)

# Introduction (1 page)

# Analysis Plan (2 pages)

**State the methods used**

**Explain why those methods were chosen**


# Descriptive and Univariate Analyses (3 pages)

**Basic descriptive analyses:** means, medians, percentages, etc. 

**Graphics:** histograms, scatter plots, etc. 
You do not need to be complete here, aim for including the descriptive results which best set up the inferential analyses which are to follow.

## Data Cleaning

```{r, echo = F}

# Loading packages
library(dplyr)

# Read in the COVID-19 line list from HK --------------------------------------------------------
Linelist <- read.csv("Hong Kong Line List.csv", header = T)

# Create binary variables to prepare for aggregationn
linelist <- Linelist %>%
              mutate(
                Male = ifelse(Gender == "M", 1, 0),
                Cases = 1,
                Deaths = ifelse(Linelist$Outcomes == "Deceased", 1, 0),
                Imported = ifelse(Linelist$Case.classification == "Imported", 1, 0),
                Resident = ifelse(Linelist$HK.residents == "HK resident", 1, 0),
                Proxy = ifelse(Linelist$Proxy == "Yes", 1, 0)
              )

# Rearrange dataframe to prepare for aggregation
linelist <- linelist %>%
              select(Case.ID, Region, District, Male, Age,
                     Cases, Deaths, Proxy, Imported, Resident)

# Aggregate dataframe by Region, District, Gender
linelist.agg <- linelist %>%
                  group_by(Region, District) %>%
                  summarise(Cases = sum(Cases),
                            Deaths = sum(Deaths),
                            Age = mean(Age),
                            Prop.male = sum(Male)/sum(Cases),
                            Proxy = sum(Proxy),
                            Imported = sum(Imported),
                            Resident = sum(Resident))

# Read in covariates dataset --------------------------------------------------------------------
Covariates <- read.csv("Hong Kong Covariates V2.csv")

# Merging the line list and covariates datasets by district -------------------------------------
Data <- merge(x = linelist.agg, y = Covariates, by = "District")

# Selecting which covariates to include ---------------------------------------------------------
Data$Pct.Male <- Data$Male.Count/Data$Total.Population*100
Data$Rate <- (Data$Cases/Data$Total.Pop)*100000
Data$N.Households <- as.numeric(Data$No..households)
data.clean <- Data %>%
  select(Region = Region.x, 
         District, 
         Cases,
         Rate, 
         Deaths, 
         Pct.Male,
         Total.Pop = Total.Population,
         Area.km2 = Area_km2,
         Pop.Density, 
         Pct.Labor = prop.labor.force,
         Pct.Male.Labor = Male.labor.prop,
         N.Hospital = Num_hosp,
         N.Hospital.Beds = Num_beds,
         Monthly.Income = Monthly.income..HKD.,
         N.Households,
         Pct.0.14 = Pct_0.14,
         Pct.15.24 = Pct_15.24,
         Pct.25.64 = Pct_25.64,
         Pct.65 = Pct_65.,
         Pct.Sec.Educ = Pct_Sec.Educ,
         Pct.Post.Sec = Pct_PostSec.w..degree)
```

## Boxplots by district and region

```{r, echo = F}
library(ggplot2)
library(gridExtra)
library(ggthemes)
library(pander)

#Plots of variables by Region


# create graphing function
HK.district.boxplots <- function(df, na.rm = TRUE, ...){
  
  # create for loop to produce ggplot2 graphs 
  for (i in seq_along(names(df[,3:ncol(df)]))) { 
    
    # create plot for each district in df 
    plot <- 
      ggplot(df,
             aes(Region, df[,i],group = District, colour = Region)) + 
      
      geom_boxplot(size=6, notch = T) +
      
      theme_pander() +
      theme(legend.position="none") + 
      labs(y="Value")+
      
      ggtitle(paste(names(Covariates[i]), '\n', 
                    "By Region \n",
                    sep=''))

    # print plots to screen
    print(plot)
  }
}

# run graphing function on long df
HK.district.boxplots(Covariates)
```

## Boxplot by region

```{r, echo = F}


# create graphing function
HK.region.boxplots <- function(df, na.rm = TRUE, ...){
  
  # create for loop to produce ggplot2 graphs 
  for (i in seq_along(names(df[,3:ncol(df)]))) { 
    
    # create plot for each district in df 
    plot <- 
      ggplot(df,
             aes( x=Region, y=df[,i], fill = Region)) + 
      
      geom_boxplot(size=1, notch = F) +
      
      theme_pander() +
      theme(legend.position="none") + 
      labs(y="Value")
      
      ggtitle(paste(names(covariates[i]), '\n', 
                    "By Region \n",
                    sep=''))

    # print plots to screen
    print(plot)
  }
}

# run graphing function on long df
HK.region.boxplots(covariates)


```

## Histograms

```{r, echo = F}

# create graphing function
HK.histogram <- function(df, na.rm = TRUE, ...){
  
  # create for loop to produce ggplot2 graphs 
  for (i in seq_along(names(df[,3:ncol(df)]))) { 
    
    # create plot for each district in df 
    plot <- ggplot(df, aes(df[,i])) + 
      geom_bar(position="dodge", aes(fill=Region, size=2) )+
      #facet_wrap(~Region)
      theme_pander() +
      theme(legend.position="none") + 
      labs(y="Value", x= paste(names(Covariates[i])))+
      
      ggtitle(paste(names(Covariates[i]), '\n', 
                    "By Region \n",
                    sep=''))
    # print plots to screen
    print(plot)
  }
}

# run graphing function on long df
HK.histogram(Covariates)
```

# Exploratory analysis

```{r}
# Loading packages
library(ggplot2); library(tidyr); library(gridExtra)

# Histograms ------------------------------------------------------------------------------------
data.clean %>% 
  select(Cases, Rate, Pop.Density, Pct.Male, 
         Pct.0.14, Pct.15.24, Pct.25.64, Pct.65, 
         Monthly.Income, Pct.Labor, Pct.Male.Labor, N.Households,
         Pct.Sec.Educ, Pct.Post.Sec, N.Hospital, N.Hospital.Beds) %>%
  gather() %>%                             
  ggplot(aes(value)) +                     
    facet_wrap(~key, scales = "free") +    
    geom_histogram(bins = 5) +
    xlab("") + ylab("Frequency")

# FINAL DATASET ---------------------------------------------------------------------------------
data <- data.clean %>% 
          select(District, Cases, Rate, Pop.Density, Pct.Male, 
                 Pct.0.14, Pct.15.24, Pct.25.64, Pct.65, 
                 Monthly.Income, Pct.Labor, Pct.Male.Labor, N.Households,
                 Pct.Sec.Educ, Pct.Post.Sec, N.Hospital, N.Hospital.Beds) 
summary(data)
str(data)

# Pairs plot to check for correlation -----------------------------------------------------------
pairs(data)

# Coordinates by district -----------------------------------------------------------------------
HKcoords <- read.csv("HK_coords.csv", header = T)
HKcoords <- HKcoords[order(HKcoords$District), ]
data$Lat <- HKcoords$Lat
data$Long <- HKcoords$Long

# Creating maps for exploratory analysis --------------------------------------------------------
library(spdep); library(rgdal); library(maptools)
library(sp); library(RColorBrewer); library(classInt)

# Adding variables in shapefile
shp_HK = readOGR("shp_HK/Hong_Kong_18_Districts.shp", stringsAsFactors = FALSE)
shp_HK = shp_HK[order(shp_HK$ENAME),]
shp_HK$Lat = data$Lat
shp_HK$Long = data$Long
shp_HK$Cases = data$Cases
shp_HK$Rate = data$Rate
shp_HK$TotalPop = Data$Total.Population
shp_HK$PopDens = data$Pop.Density
shp_HK$PropMale = data$Pct.Male/100
shp_HK$PropFemale = (100-data$Pct.Male)/100
shp_HK$Prop0_14 = data$Pct.0.14/100
shp_HK$Prop15_24 = data$Pct.15.24/100
shp_HK$Prop25_64 = data$Pct.25.64/100
shp_HK$Prop65 = data$Pct.65/100
shp_HK$Income = data$Monthly.Income
shp_HK$Housing = data$N.Households
shp_HK$Hosp = data$N.Hospital
shp_HK$HospBeds = data$N.Hospital.Beds
shp_HK$SecEduc = data$Pct.Sec.Educ/100
shp_HK$PostSec = data$Pct.Post.Sec/100
shp_HK$PropLabor = data$Pct.Labor/100
shp_HK$PropMaleLabor = data$Pct.Male.Labor

# Converting shapefile data to dataframe object
# merge the "fortified" data with the data from our spatial object
shp_HK$id = rownames(shp_HK@data)
shp = fortify(shp_HK)
shp_HK.df = merge(shp, shp_HK@data, by = "id")

# Maps of Response and Covariates, by District --------------------------------------------------

# Total COVID-19 cases (as continuous variable) -------------------------------------------------
ggplot(data = shp_HK.df, aes(x = long, y = lat, group = group), colour = "black", fill = NA) +
  geom_polygon(data = shp_HK.df, aes(fill = Cases)) + 
  ggtitle("Total COVID-19 cases, by district") +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7") +
  theme(legend.title = element_blank(),
        legend.justification=c(1,0), 
        legend.position=c(1,0),
        plot.title = element_text(hjust = 0.5),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_blank(),
        panel.grid = element_blank(),
        axis.title = element_blank(), 
        panel.background = element_blank()) +
    coord_fixed(1.3)

# Total COVID-19 cases (as discrete variable) ---------------------------------------------------
brks <-classIntervals(shp_HK$Cases, n=5, style="quantile")
brks <- brks$brks
shp_HK.df$CasesCat[shp_HK.df$Cases < 10] = 0
shp_HK.df$CasesCat[shp_HK.df$Cases >= 10 & shp_HK.df$Cases < 15] = 1
shp_HK.df$CasesCat[shp_HK.df$Cases >= 15 & shp_HK.df$Cases < 20] = 2
shp_HK.df$CasesCat[shp_HK.df$Cases >= 20 & shp_HK.df$Cases < 43] = 3
shp_HK.df$CasesCat[shp_HK.df$Cases >= 43] = 4
shp_HK.df$CasesCat = factor(shp_HK.df$CasesCat, levels = 0:4, labels = c("<10", "10-14", "15-19", "20-42", ">42"))

plota =
  ggplot(data = shp_HK.df, aes(x = long, y = lat, group = group), colour = "black", fill = NA) +
  geom_polygon(data = shp_HK.df, aes(fill = CasesCat)) + 
  scale_fill_brewer(palette = "YlOrRd") +
  ggtitle("Total COVID-19 cases") +
  theme(legend.title = element_blank(),
        legend.justification=c(1,0), 
        legend.position=c(1,0),
        plot.title = element_text(hjust = 0.5),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_blank(),
        panel.grid = element_blank(),
        axis.title = element_blank(), 
        panel.background = element_blank()) +
    coord_fixed(1.3)

# COVID-19 rate per 100,000 ---------------------------------------------------------------------
brks <-classIntervals(shp_HK$Rate, n=5, style="quantile")
brks <- brks$brks
shp_HK.df$RateCat[shp_HK.df$Rate < brks[2]] = 0
shp_HK.df$RateCat[shp_HK.df$Rate >= brks[2] & shp_HK.df$Rate < brks[3]] = 1
shp_HK.df$RateCat[shp_HK.df$Rate >= brks[3] & shp_HK.df$Rate < brks[4]] = 2
shp_HK.df$RateCat[shp_HK.df$Rate >= brks[4] & shp_HK.df$Rate < brks[5]] = 3
shp_HK.df$RateCat[shp_HK.df$Rate >= brks[5]] = 4
shp_HK.df$RateCat = factor(shp_HK.df$RateCat, levels = 0:4, labels = c("<2.5", "2.5-3.2", "3.2-4.5", "4.5-13.6", ">13.6"))

plota2 =
  ggplot(data = shp_HK.df, aes(x = long, y = lat, group = group), colour = "black", fill = NA) +
  geom_polygon(data = shp_HK.df, aes(fill = RateCat)) + 
  scale_fill_brewer(palette = "YlOrRd") +
  ggtitle("Rate of COVID-19 per 100,000") +
  theme(legend.title = element_blank(),
        legend.justification=c(1,0), 
        legend.position=c(1,0),
        plot.title = element_text(hjust = 0.5),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_blank(),
        panel.grid = element_blank(),
        axis.title = element_blank(), 
        panel.background = element_blank()) +
    coord_fixed(1.3)

grid.arrange(plota, plota2)

# Population density ----------------------------------------------------------------------------
plotb = 
  ggplot(data = shp_HK.df, aes(x = long, y = lat, group = group), colour = "black", fill = NA) +
  geom_polygon(data = shp_HK.df, aes(fill = PopDens)) + 
  ggtitle("Population density") +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7") +
  theme(legend.title = element_blank(),
        legend.justification=c(1,0), 
        legend.position=c(1,0),
        plot.title = element_text(hjust = 0.5),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_blank(),
        panel.grid = element_blank(),
        axis.title = element_blank(), 
        panel.background = element_blank()) +
    coord_fixed(1.3)

# Male population -------------------------------------------------------------------------------
plotc = 
  ggplot(data = shp_HK.df, aes(x = long, y = lat, group = group), colour = "black", fill = NA) +
  geom_polygon(data = shp_HK.df, aes(fill = PropMale)) + 
  ggtitle("Proportion of males") +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7") +
  theme(legend.title = element_blank(),
        legend.justification=c(1,0), 
        legend.position=c(1,0),
        plot.title = element_text(hjust = 0.5),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_blank(),
        panel.grid = element_blank(),
        axis.title = element_blank(), 
        panel.background = element_blank()) +
    coord_fixed(1.3)

# Female population ------------------------------------------------------------------------------
plotd = 
  ggplot(data = shp_HK.df, aes(x = long, y = lat, group = group), colour = "black", fill = NA) +
  geom_polygon(data = shp_HK.df, aes(fill = PropFemale)) + 
  ggtitle("Proportion of females") +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7") +
  theme(legend.title = element_blank(),
        legend.justification=c(1,0), 
        legend.position=c(1,0),
        plot.title = element_text(hjust = 0.5),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_blank(),
        panel.grid = element_blank(),
        axis.title = element_blank(), 
        panel.background = element_blank()) +
    coord_fixed(1.3)

# Population of 65+ -----------------------------------------------------------------------------
plote = 
  ggplot(data = shp_HK.df, aes(x = long, y = lat, group = group), colour = "black", fill = NA) +
  geom_polygon(data = shp_HK.df, aes(fill = Prop65)) + 
  ggtitle("Proportion of 65 and above") +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7") +
  theme(legend.title = element_blank(),
        legend.justification=c(1,0), 
        legend.position=c(1,0),
        plot.title = element_text(hjust = 0.5),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_blank(),
        panel.grid = element_blank(),
        axis.title = element_blank(), 
        panel.background = element_blank()) +
    coord_fixed(1.3)

# Population of 15-24 ---------------------------------------------------------------------------
plotf =
  ggplot(data = shp_HK.df, aes(x = long, y = lat, group = group), colour = "black", fill = NA) +
  geom_polygon(data = shp_HK.df, aes(fill = Prop15_24)) + 
  ggtitle("Proportion of 15-24 years old") +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7") +
  theme(legend.title = element_blank(),
        legend.justification=c(1,0), 
        legend.position=c(1,0),
        plot.title = element_text(hjust = 0.5),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_blank(),
        panel.grid = element_blank(),
        axis.title = element_blank(), 
        panel.background = element_blank()) +
    coord_fixed(1.3)

grid.arrange(plota2, plotb, plotc, plotd, plote, plotf)

# Population of 0-14 years old ------------------------------------------------------------------
plotg =
  ggplot(data = shp_HK.df, aes(x = long, y = lat, group = group), colour = "black", fill = NA) +
  geom_polygon(data = shp_HK.df, aes(fill = Prop0_14)) + 
  ggtitle("Proportion of 0-14 years old") +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7") +
  theme(legend.title = element_blank(),
        legend.justification=c(1,0), 
        legend.position=c(1,0),
        plot.title = element_text(hjust = 0.5),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_blank(),
        panel.grid = element_blank(),
        axis.title = element_blank(), 
        panel.background = element_blank()) +
    coord_fixed(1.3)

# Population of 25-64 years old ----------------------------------------------------------------
ploth =
  ggplot(data = shp_HK.df, aes(x = long, y = lat, group = group), colour = "black", fill = NA) +
  geom_polygon(data = shp_HK.df, aes(fill = Prop25_64)) + 
  ggtitle("Proportion of 25-64 years old") +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7") +
  theme(legend.title = element_blank(),
        legend.justification=c(1,0), 
        legend.position=c(1,0),
        plot.title = element_text(hjust = 0.5),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_blank(),
        panel.grid = element_blank(),
        axis.title = element_blank(), 
        panel.background = element_blank()) +
    coord_fixed(1.3)

# Proportion of Post-Sec Educ ------------------------------------------------------------------
ploti =
  ggplot(data = shp_HK.df, aes(x = long, y = lat, group = group), colour = "black", fill = NA) +
  geom_polygon(data = shp_HK.df, aes(fill = PostSec)) + 
  ggtitle("Proportion with Post-Secondary Education") +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7") +
  theme(legend.title = element_blank(),
        legend.justification=c(1,0), 
        legend.position=c(1,0),
        plot.title = element_text(hjust = 0.5),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_blank(),
        panel.grid = element_blank(),
        axis.title = element_blank(), 
        panel.background = element_blank()) +
    coord_fixed(1.3)

# Proportion of Secondary education and higher -------------------------------------------------
plotj =
  ggplot(data = shp_HK.df, aes(x = long, y = lat, group = group), colour = "black", fill = NA) +
  geom_polygon(data = shp_HK.df, aes(fill = SecEduc)) + 
  ggtitle("Proportion with Secondary Education and higher") +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7") +
  theme(legend.title = element_blank(),
        legend.justification=c(1,0), 
        legend.position=c(1,0),
        plot.title = element_text(hjust = 0.5),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_blank(),
        panel.grid = element_blank(),
        axis.title = element_blank(), 
        panel.background = element_blank()) +
    coord_fixed(1.3)

# Number of housing units ----------------------------------------------------------------------
plotk =
  ggplot(data = shp_HK.df, aes(x = long, y = lat, group = group), colour = "black", fill = NA) +
  geom_polygon(data = shp_HK.df, aes(fill = Housing)) + 
  ggtitle("Number of Households") +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7") +
  theme(legend.title = element_blank(),
        legend.justification=c(1,0), 
        legend.position=c(1,0),
        plot.title = element_text(hjust = 0.5),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_blank(),
        panel.grid = element_blank(),
        axis.title = element_blank(), 
        panel.background = element_blank()) +
    coord_fixed(1.3)

# Average number of beds per hospital ---------------------------------------------------------
plotl =
  ggplot(data = shp_HK.df, aes(x = long, y = lat, group = group), colour = "black", fill = NA) +
  geom_polygon(data = shp_HK.df, aes(fill = HospBeds)) + 
  ggtitle("Average number of beds per hospital") +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7") +
  theme(legend.title = element_blank(),
        legend.justification=c(1,0), 
        legend.position=c(1,0),
        plot.title = element_text(hjust = 0.5),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_blank(),
        panel.grid = element_blank(),
        axis.title = element_blank(), 
        panel.background = element_blank()) +
    coord_fixed(1.3)

# Number of hospital ---------------------------------------------------------------------------
plotm =
  ggplot(data = shp_HK.df, aes(x = long, y = lat, group = group), colour = "black", fill = NA) +
  geom_polygon(data = shp_HK.df, aes(fill = Hosp)) + 
  ggtitle("Number of hospitals") +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7") +
  theme(legend.title = element_blank(),
        legend.justification=c(1,0), 
        legend.position=c(1,0),
        plot.title = element_text(hjust = 0.5),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_blank(),
        panel.grid = element_blank(),
        axis.title = element_blank(), 
        panel.background = element_blank()) +
    coord_fixed(1.3)

grid.arrange(plotg, ploth, ploti, plotj, plotk, plotl, ncol = 2)
# Income ----------------------------------------------------------------------------------------
plotn =
  ggplot(data = shp_HK.df, aes(x = long, y = lat, group = group), colour = "black", fill = NA) +
  geom_polygon(data = shp_HK.df, aes(fill = Income)) + 
  ggtitle("Monthly Income") +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7") +
  theme(legend.title = element_blank(),
        legend.justification=c(1,0), 
        legend.position=c(1,0),
        plot.title = element_text(hjust = 0.5),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_blank(),
        panel.grid = element_blank(),
        axis.title = element_blank(), 
        panel.background = element_blank()) +
    coord_fixed(1.3)
```

```{r}
# BMA model selection ----------------------------------------------------------------------------
library(BMA)

# Removing country and outcome columns to convert to covariates matrix for bicreg
colnames(data)
data.X <- data[ , -c(1:3, 18:19)]

BMA.models <- bic.glm(x = data.X, y = data$Cases, glm.family = poisson(), dispersion = F)
summary(BMA.models)
BMA.models
```


# Summary of Inferential Results (3 pages)

# Conclusion (1 page)

# Appendix
